% This document is a test example of a report document in LaTeX. 

\documentclass{report}
\usepackage[utf8]{inputenc}

\title{Report}
\author{Vyoma Jani \thanks{Helped by that website I Googled}}

\begin{document}

\maketitle

\tableofcontents

\part{The First Part}

\chapter{The First Chapter}

\section{Introduction}

This is the first section. Pretty cool huh? The section will continue until you specify the next section or chapter, and then it'll start the new section or chapter.

\section{Second Section}

Sections can even have their own subsections! 

\subsection{First Subsection}

This here is a subsection of the section, in case you need to break it up even more. 

You can break it up \textit{even more} with subsubsections!

\subsubsection{First Subsubsection}

Now this is getting ridiculous. I guess we can just roll with it.

Now we will add some tables!

Here is a basic table, with no borders whatsoever. 

\begin{center}

\begin{tabular}{c rl}

cell1 & cell2 & cell3 \\
cell4 & cell5 & cell6 \\
cell7 & cell8 & cell9

\end{tabular}

\end{center}

What if we wanted vertical borders?

\begin{center}

\begin{tabular}{ |c|||r l| }

cell1 & cell2 & cell3 \\
cell4 & cell5 & cell6 \\
cell7 & cell8 & cell9

\end{tabular}

\end{center}

The above example has a few vertical borders.

What if we want horizontal borders?

\begin{center}

\begin{tabular}{c r l}

cell1 & cell2isthis & cell3 \\
\hline
cell4 & cell5 & cell6isthis \\
cell7isthis & cell8 & cell9 \\
\hline
\hline

\end{tabular}

\end{center}

We can also add captions, labels, and references to the tables. 

Table \ref{table:data} is an example of these referenced \LaTeX{} elements.
 
\begin{table}[h!]

\centering

\begin{tabular}{||c c c c||} 

 \hline
 Col1 & Col2 & Col2 & Col3 \\ 
 \hline\hline
 1 & 6 & 87837 & 787 \\ 
 2 & 7 & 78 & 5415 \\
 3 & 545 & 778 & 7507 \\
 4 & 545 & 18744 & 7560 \\
 5 & 88 & 788 & 6344 \\
 \hline
 
\end{tabular}

\caption{Table to test captions and labels}

\label{table:data}

\end{table}


\section*{Unnumbered Section}

Not all sections need to be numbered! Or maybe you don't want any of the sections to be numbered!

\paragraph{First Paragraph} 

I guess if you do want to go smaller than a subsubsection, then you use paragraphs. 

\subparagraph{First Subparagraph}

And if a paragraph isn't enough, we break it up into subparagraphs.

\end{document}

